`{peacesciencer}`: An R Package for Quantitative Peace Science Research

### 2022-01-12 manuscript/appendix.Rmd
rename directory

@@

>>>>

# Vignette: How `{peacesciencer}` Coerces Dispute-Year Data into Dyad-Year Data

```{r child = '../vignettes/coerce-dispute-year-dyad-year.Rmd', echo=TRUE}
```

@@

# Vignette: A Discussion of Correlates of War and Gleditsch-Ward Systems and `{peacesciencer}`

```{r child = '../vignettes/state-systems.Rmd', echo=TRUE}
```

### 2022-01-12 manuscript/ms.Rmd
rename directory

This will open a documentation file for this function, which is itself quite verbose and informative for the user about what the function is doing. In this case, the documentation file will show there are three arguments in this function, each with built-in defaults. This function will allow the user to choose a state system for which they want state-years (`system`, which accepts either "cow" or "gw" for Correlates of War [CoW] state system data or Gleditsch-Ward [G-W] state system data and defaults to "cow"), whether they want to extend the state system to the most recently concluded calendar year (`mry`, which defaults to TRUE), and whether they may want to additionally subset the years to a more narrow temporal domain they may already have in mind (`subset_years`, which defaults to no subset of the data, returning all possible state-years). If the user simply ran the function with no overrides, the function would return all Correlates of War state-years from 1816 to the most recent year (2020, as of writing).

>>>>

This will open a documentation file for this function, which is itself quite verbose and informative for the user about what the function is doing. In this case, the documentation file will show there are three arguments in this function, each with built-in defaults. This function will allow the user to choose a state system for which they want state-years (`system`, which accepts either "cow" or "gw" for Correlates of War [CoW] state system data or Gleditsch-Ward [G-W] state system data and defaults to "cow"), whether they want to extend the state system to the most recently concluded calendar year (`mry`, which defaults to TRUE), and whether they may want to additionally subset the years to a more narrow temporal domain they may already have in mind (`subset_years`, which defaults to no subset of the data, returning all possible state-years). If the user simply ran the function with no overrides, the function would return all Correlates of War state-years from 1816 to the most recent year (2021, as of writing).
